---
title: "Learning R"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

Prep
```{r}
library("stringr")
```


# Practice problems 
Sourced from Crump Lab at Brooklyn College

Find the sum of all the integer numbers from 1 to 100.

```{r}
sum(1:100)


sum<-0
for (i in 1:100){
  sum<-sum+i
}
```


Write a function to find the sum of all integers between any two values.
```{r}
value.sum<- function(x,y){
  sum(x:y)
}
value.sum(1,100)
```


List all of the odd numbers from 1 to 100.
```{r}
seq(1,100,2)

num<-0
for (i in 1:100){
  num<-num+1
if (num%%2 != 0) 
  print(num)
}
#?corrected num+i --> num +1

```

List all of the prime numbers from 1 to 1000.

```{r}

prime_numbers <- function(n){
  if(n>=2){ 
    x=seq(2,n)
Prime=c()
for(i in seq(2,n)){
  if(any(x==i)){
    Prime=c(Prime,i)
    #creating object to store prime numbers
    x=c(x[(x%%i) !=0])
    #within vector x, if number in position does not divide evenly, print
  }
}
return(Prime)}
  else
  {
  stop()
  }
  #using nested functions
}
prime_numbers(1000)
```

Generate 100 random numbers. 
```{r}
runif(100)
#pseudorandom numbers across a uniform distribution where all numbers are equally probable 

set.seed(666)
runif(100)
```
Count the number of characters in a string variable

```{r}
#using stringr package 
a<-"de la douleur, de l'ennui et de la mort"
str_count(a, "e")

str_count(a, "de")
```


Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: mean, mode, median, range, standard deviation

```{r}
my_mean<-function(x){
sum(x)/length(x)}
my_mean(c(1,2,3))

my_mean.2<- function(x){
  total_sum<-0
  for(i in x){
    total_sum<-total_sum+i
  }#using indexing
  return(total_sum/length(x))
}
my_mean(c(1,2,3))
```


```{r}
nchar("Jamie Fox")
celebrity01<-"Jamie Fox"
nchar(celebrity01)

string<-"Hello world"
(String<-unlist(strsplit(string,split="")))
length(String)

#not possible to count elements in a list ?
```

Count the number of words in a string variable

```{r}
x1<-c("Down by the corner")
sapply(strsplit(x1," "), length)
```


Create a variable that stores a 20x20 matrix of random numbers
```{r}
matrix(runif(400), nrow=20, ncol=20, byrow=TRUE)
```
Read a .txt file or .csv file into a variable
```{r}
Spotify_samplelib<-read.csv("C:/Users/12055/Documents/R/Kaggle data sets/spotify_dataset.csv")
```

Count the number of sentences in a string variable.
```{r}
library(quanteda)
nsentence("Tout peut s'oublier ! Qui s'enfuit deja.")
```


Do a logical test to see if one word is found within the text of another string variable.


Put the current computer time in milliseconds into a variable

Measure how long a piece of code takes to run by measuring the time before the code is run, and after the code is run, and taking the difference to find the total time


Output the contents of a variable to a .txt file


Output any matrix to a txt file using commas or tabs to separate column values, and new lines to separate row values


Project Euler
<<If we list all the natural numbers below 10 that are multiples of 3 or 5, we get 3,5, 6, and 9. The sum of these multiples is 23.
Find the sum of all the multiples of 3 or 5 below 1000.>> 







