---
title: "Learning R"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: true
    smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Crump lab practice problems

## Problem 1

Find the sum of all the integer numbers from 1 to 100.

```{r}
sum(1:100)


sum<-0
for (i in 1:100){
  sum<-sum+i
}
```


## Problem 2

Write a function to find the sum of all integers between any two values.
```{r}
value.sum<- function(x,y){
  sum(x:y)
}
value.sum(1,100)
```


## Problem 3

List all of the odd numbers from 1 to 100.
```{r}
seq(1,100,2)

num<-0
for (i in 1:100){
  num<-num+1
if (num%%2 != 0) 
  print(num)
}
#?corrected num+i --> num +1

```

## Problem 4

List all of the prime numbers from 1 to 1000.

```{r}

prime_numbers <- function(n){
  if(n>=2){ 
    x=seq(2,n)
Prime=c()
for(i in seq(2,n)){
  if(any(x==i)){
    Prime=c(Prime,i)
    #creating object to store prime numbers
    x=c(x[(x%%i) !=0])
    #within vector x, if number in position does not divide evenly, print
  }
}
return(Prime)}
  else
  {
  stop()
  }
  #using nested functions
}
prime_numbers(1000)
```

Generate 100 random numbers. 
```{r}
runif(100)
#pseudorandom numbers across a uniform distribution where all numbers are equally probable 

set.seed(666)
runif(100)
```

## 10

Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: mean, mode, median, range, standard deviation

```{r}
my_mean<-function(x){
sum(x)/length(x)}
my_mean(c(1,2,3))

my_mean.2<- function(x){
  total_sum<-0
  for(i in x){
    total_sum<-total_sum+i
  }#using indexing
  return(total_sum/length(x))
}
my_mean(c(1,2,3))


my_median<-function(x){
  #if odd
position.odd<-(length(x)/2)
return[position.odd]
#if even
#position.even<-((length(x)/2)+((length(x)/2)+1
#return([position.even])
#print(median.position)
}

#my_median(c(1,2,3,4,5))
#my_median(c(1,2,3,4))

my_range<-function(x){
  v<- c(x)
v2<-sort(v)
range<-c(v2[1], v2[length(v2)])
print(range)}

range(1,20,4,6,8,3)
```


## 11

Count the number of characters in a string variable
```{r}
nchar("Jamie Fox")
celebrity01<-"Jamie Fox"
nchar(celebrity01)

string<-"Hello world"
(String<-unlist(strsplit(string,split="")))
length(String)

#not possible to count elements in a list ?
```


## 12

Count the number of words in a string variable

```{r}
x1<-c("Down by the corner")
sapply(strsplit(x1," "), length)
```


Create a variable that stores a 20x20 matrix of random numbers
```{r}
matrix(runif(400), nrow=20, ncol=20, byrow=TRUE)
```

## 13

Count the number of sentences in a string variable.

```{r}

```


## 14 

Count the number of times a specific character occurs in a string variable
```{r}
"de la douleur, de l'ennui et de la mort"
```


## 15

Do a logical test to see if one word is found within the text of another string variable.

## 16

Put the current computer time in milliseconds into a variable

## 17

Measure how long a piece of code takes to run by measuring the time before the code is run, and after the code is run, and taking the difference to find the total time

## 18

Read a .txt file or .csv file into a variable

## 19

Output the contents of a variable to a .txt file

## 21

Output any matrix to a txt file using commas or tabs to separate column values, and new lines to separate row values









