---
title: "Learning R"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Crump lab practice problems

## Problem 1

Find the sum of all the integer numbers from 1 to 100.

```{r}
sum(1:100)


sum<-0
for (i in 1:100){
  sum<-sum+i
}
```


## Problem 2

Write a function to find the sum of all integers between any two values.
```{r}
value.sum<- function(x,y){
  sum(x:y)
}
value.sum(1,100)
```


## Problem 3

List all of the odd numbers from 1 to 100.
```{r}
seq(1,100,2)

num<-0
for (i in 1:100){
  num<-num+i
if (num%%2 != 0) 
  print(num)
}
#best attempt using mod

```
# Problem 4

List all of the prime numbers from 1 to 1000.

```{r}
#developing algorithm based on sieve of Eratosthenes

prime_numbers <- function(n){
  if(n>=2){
    
  }
}

prime_numbers(1000)
```

# Generate 100 random numbers. 
```{r}
?runif
#why runif over rnorm ?

runif(100)
```


# Example problems


So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation =1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

## Example 1

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```


## Example 2

Do simple math with numbers, addition, subtraction, multiplication, division

```{r}
1+2
2*5
5/3
(1+6+4)/5

```

## Example 3

Put numbers into variables, do simple math on the variables

```{r}
a<-1
b<-2
a+b

d<-c(1,2,3)
e<-c(5,6,7)
d+e
d*e
d/e

```


## Example 4

Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r}
# for loop solution
# i becomes the number 1 to 100 at each step of the loop


a <- length(100) # make empty variable, set length to 100
for (i in 1:100){
  a[i] <-i #assigns the number in i, to the ith index of a
}

print(a)

# for loop solution #2

a<-c() #create empty variable using combine command
for (i in 1:100){
  a<-c(a,i) # keeps combining a with itself and the new number in i
}
print(a)

# seq solution
a <- seq(1,100,1) # look up help for seq using ?seq() in console
print(a)

```




